Interpretable Neural Networks using EAGGA

### 2025-03-14 paper/main.tex
add monotonicity constraint equations

      * given layer input $\boldsymbol{x}$ and omitting bias

@@

@@

- Figure \ref{fig-test-dhvs} suggests comparable performance to XGBoost EAGGA
  * unfortunately no comparison to unrestricted NN
  * would not be sensible, as NF, NI, NNM would be 1, hence hypervolume = 0, as values along 3 dimensions would be at reference point

>>>>

      * given layer input $\boldsymbol{x}$ and w.l.o.g. omitting bias

@@

      * consider vector form computation of hidden neuron $\boldsymbol{o}_{\text{in}}^{(l)}\in\mathbb{R}^{p^{(l)}}$ of layer $l$
        - $\boldsymbol{o}_{\text{in}}^{(l)}=\boldsymbol{W} \boldsymbol{o}_{\text{out}}^{(l-1)} + \boldsymbol{b}$
        - where $\boldsymbol{o}_{\text{in}}^{(l)}$ refers to pre-activation values, $\boldsymbol{o}_{\text{out}}^{(l)}$ to value after applying ReLU
        - weight matrix $\boldsymbol{W}\in\mathbb{R}^{p^{(l)} \times p^{(l-1)}}$
        - bias $\boldsymbol{b}\in\mathbb{R}^{p^{(l)}}$
      * definition of monotonically increasing function $f$: for $x_1\le x_2$ it must hold that $f(x_1)\le f(x_2)$
      * $\boldsymbol{W} \boldsymbol{o}_{\text{out}}^{(l-1)} + \boldsymbol{b}$ clearly only monotonic if and only if $\boldsymbol{W}\in\mathbb{R}_{0+}{p^{(l-1)}\times p^{(l)}}$
        - where $\mathbb{R}_{0+}=[0,\infty)$
        - hence weight clipping necessary, bias clipping not because only constant term
      * $\boldsymbol{o}_{\text{out}}^{(l)}=ReLU(\boldsymbol{o}_{\text{in}}^{(l)})=\max(0,\boldsymbol{o}_{\text{in}}^{(l)})$ monotonic

@@

- Figure \ref{fig-test-dhvs}
  * suggests comparable performance to XGBoost EAGGA
  * did not compare to unrestricted NN, would not be sensible, as NF, NI, NNM would be 1, hence hypervolume = 0, as values along 3 dimensions would be at reference point
  * as XGBoost EAGGA, NN EAGGA consistently outperforms union of competitors as evident from \citep[Figure 2]{EAGGA}
  * unfortunately due to time constraints no own union comparison with NN instead of XGBoost
